\textbf{Research Proposal for the NPC Fellowship}\\

### 2016-09-15 NPCProposal2016/proposal_Shih-Kai_Lin.tex
more specific funding request and lab contact person

GENIE physics modeling is particularly interesting among the items. There is evidence of 2p2h effects also in the RHC data~\cite{Bashar:2016_1}. A data/MC comparison shows that the inclusion of MEC effect leads to better data MC agreement for the forward horn current (FHC) data. However, the current MEC model for $\bar{\nu}_\mu$ only partially improves the data/MC agreement - disagreement is greater at low visible hadronic energy. One hypothesis is that the NOvA detectors might see neutrons, and methods for measuring and reconstructing neutrons are under investigation. Our group at Colorado State University plans to take on this problem by looking at the event topology at the very low visible hadronic energy and see if any event topology in data but not in MC can be identified. MEC effects in other variables such as the invariant hadronic mass $W$ and the four-momentum transfer $Q$ will also be pursued.\newline

@@

The DDT code base has been managed in a per package manner, meaning that the individual author of the packages takes the responsibility that his or her code builds and takes sensible data. This model of DDT package management has become cumbersome and prevents careful validation from routinely occurring. One of the priorities of the DDT group is to reorganize the DDT software packages to centralize common algorithms like clustering and tracking. Such improvement will make the code easier to manage and make it easier for new group members to quickly become engaged in trigger development. The DDT and DAQ groups also plan to migrate to the SRT build system from the multi release build (MRB) system. Using SRT could avoid inconsistencies between the online and the offline DDT builds. I am taking the role as the manager of the DDT code base and working on the build system migration.\newline
%However, past experience shows this way sometimes leads to code redundancy, such as a same reconstruction algorithm being implemented in different packages. Besides, the lack of validation procedures also resulted in nonsensical data. The DDT group has come up with the idea of cleaning up the DDT codebase, making it more modular, and having a person to watch over the consistency between packages and tag releases. Also, the developers are requested to follow a validation procedure before deployment, and a person will be supervising this process. I am taking this role as the code manager. Furthermore, since the current DDT uses multi release build (MRB) as its build system, which leads to inconsistency between the online and the offline DDT builds, the DAQ and the DDT group plan to migrate the build system back to the older SRT. I will also be working on this together with people from DAQ and DDT group.\newline

Office space with a computer for code development and software for data analysis are readily accessible. To cover my travel and local expenses, I am requesting a budget of \$\underline{12,000} for a six-month period.
%\$\underline{\hspace{2cm}}.
\clearpage

>>>>

GENIE physics modeling is particularly interesting among the items. There is evidence of 2p2h effects also in the RHC data~\cite{Bashar:2016_1}. A data/MC comparison shows that the inclusion of MEC effect leads to better data MC agreement for the forward horn current (FHC) data. However, the current MEC model for $\bar{\nu}_\mu$ only partially improves the data/MC agreement - disagreement is greater at low visible hadronic energy. One hypothesis is that the NOvA detectors might see neutrons, and methods for measuring and reconstructing neutrons are under investigation. Our group at Colorado State University plans to take on this problem by looking at the event topology at the very low visible hadronic energy and see if any event topology in data but not in MC can be identified. MEC effects in other variables such as the invariant hadronic mass $W$ and the four-momentum transfer $Q$ will also be pursued.

@@

The DDT code base has been managed in a per package manner, meaning that the individual author of the packages takes the responsibility that his or her code builds and takes sensible data. This model of DDT package management has become cumbersome and prevents careful validation from routinely occurring. One of the priorities of the DDT group is to reorganize the DDT software packages to centralize common algorithms like clustering and tracking. Such improvement will make the code easier to manage and make it easier for new group members to quickly become engaged in trigger development. The DDT and DAQ groups also plan to migrate to the SRT build system from the multi release build (MRB) system. Using SRT could avoid inconsistencies between the online and the offline DDT builds. I am taking the role as the manager of the DDT code base and working on the build system migration.
%However, past experience shows this way sometimes leads to code redundancy, such as a same reconstruction algorithm being implemented in different packages. Besides, the lack of validation procedures also resulted in nonsensical data. The DDT group has come up with the idea of cleaning up the DDT codebase, making it more modular, and having a person to watch over the consistency between packages and tag releases. Also, the developers are requested to follow a validation procedure before deployment, and a person will be supervising this process. I am taking this role as the code manager. Furthermore, since the current DDT uses multi release build (MRB) as its build system, which leads to inconsistency between the online and the offline DDT builds, the DAQ and the DDT group plan to migrate the build system back to the older SRT. I will also be working on this together with people from DAQ and DDT group.\newline
I will be working closely with one of the conveners of the NOvA near detector physics group, Jonathan Paley, on $\bar{\nu}_\mu$ interactions, and with Andrew Norman on DDT management.\newline

Office space with a computer for code development and software for data analysis are readily accessible. To cover the move from my home institution in Fort Collins to Chicago Area, which costs about \$2,400, and local expenses, which cost about \$1,600 monthly including housing and utilities, I am requesting a budget of \$\underline{12,000} for a six-month period.
%\$\underline{\hspace{2cm}}.
\clearpage
